maxent model avec xvalidation (year-based test training)

### 2019-08-30 src/AO_NAO_comparison.Rmd
laptop update

```{r}
naoraw <- read.csv("./data/env/nao_pc_monthly.csv", header = FALSE) 
head(naoraw)
```

lets give some column names. col 1  year, 2:13 are the months
```{r}
colnames(naoraw) <- c("year","Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec")
head(naoraw)
```

@@

naojanq1 <- subset(nao$year, nao$Jan <= naoq1$Jan)
write.csv(naojanq1, "../output/env/nao_jan_q1.csv")        
naofebq1 <- subset(nao$year, nao$Feb <= naoq1$Feb)
write.csv(naofebq1, "../output/env/nao_feb_q1.csv") 
naomarq1 <- subset(nao$year, nao$Mar <= naoq1$Mar)
write.csv(naomarq1, "../output/env/nao_mar_q1.csv")        
naoaprq1 <- subset(nao$year, nao$Apr <= naoq1$Apr)
write.csv(naoaprq1, "../output/env/nao_apr_q1.csv")  
naomayq1 <- subset(nao$year, nao$May <= naoq1$May)
write.csv(naomayq1, "../output/env/nao_may_q1.csv")        
naojunq1 <- subset(nao$year, nao$Jun <= naoq1$Jun)
write.csv(naojunq1, "../output/env/nao_jun_q1.csv") 
naojulq1 <- subset(nao$year, nao$Jul <= naoq1$Jul)
write.csv(naojulq1, "../output/env/nao_jul_q1.csv")        
naoaugq1 <- subset(nao$year, nao$Aug <= naoq1$Aug)
write.csv(naoaugq1, "../output/env/nao_aug_q1.csv")  
naosepq1 <- subset(nao$year, nao$Sep <= naoq1$Sep)
write.csv(naosepq1, "../output/env/nao_sep_q1.csv")        
naooctq1 <- subset(nao$year, nao$Oct <= naoq1$Oct)
write.csv(naooctq1, "../output/env/nao_oct_q1.csv") 
naonovq1 <- subset(nao$year, nao$Nov <= naoq1$Nov)
write.csv(naonovq1, "../output/env/nao_nov_q1.csv")        
naodecq1 <- subset(nao$year, nao$Dec <= naoq1$Dec)
write.csv(naodecq1, "../output/env/nao_dec_q1.csv")

@@

naojanq4 <- subset(nao$year, nao$Jan >= naoq4$Jan)
write.csv(naojanq4, "../output/env/nao_jan_q4.csv")        
naofebq4 <- subset(nao$year, nao$Feb >= naoq4$Feb)
write.csv(naofebq4, "../output/env/nao_feb_q4.csv") 
naomarq4 <- subset(nao$year, nao$Mar >= naoq4$Mar)
write.csv(naomarq4, "../output/env/nao_mar_q4.csv")        
naoaprq4 <- subset(nao$year, nao$Apr >= naoq4$Apr)
write.csv(naoaprq4, "../output/env/nao_apr_q4.csv")  
naomayq4 <- subset(nao$year, nao$May >= naoq4$May)
write.csv(naomayq4, "../output/env/nao_may_q4.csv")        
naojunq4 <- subset(nao$year, nao$Jun >= naoq4$Jun)
write.csv(naojunq4, "../output/env/nao_jun_q4.csv") 
naojulq4 <- subset(nao$year, nao$Jul >= naoq4$Jul)
write.csv(naojulq4, "../output/env/nao_jul_q4.csv")        
naoaugq4 <- subset(nao$year, nao$Aug >= naoq4$Aug)
write.csv(naoaugq4, "../output/env/nao_aug_q4.csv")  
naosepq4 <- subset(nao$year, nao$Sep >= naoq4$Sep)
write.csv(naosepq4, "../output/env/nao_sep_q4.csv")        
naooctq4 <- subset(nao$year, nao$Oct >= naoq4$Oct)
write.csv(naooctq4, "../output/env/nao_oct_q4.csv") 
naonovq4 <- subset(nao$year, nao$Nov >= naoq4$Nov)
write.csv(naonovq4, "../output/env/nao_nov_q4.csv")        
naodecq4 <- subset(nao$year, nao$Dec >= naoq4$Dec)
write.csv(naodecq4, "../output/env/nao_dec_q4.csv")

@@

aojanq1 <- subset(ao$X, ao$Jan <= aoq1$Jan)
write.csv(aojanq1, "../output/env/ao_jan_q1.csv")        
aofebq1 <- subset(ao$X, ao$Feb <= aoq1$Feb)
write.csv(aofebq1, "../output/env/ao_feb_q1.csv") 
aomarq1 <- subset(ao$X, ao$Mar <= aoq1$Mar)
write.csv(aomarq1, "../output/env/ao_mar_q1.csv")        
aoaprq1 <- subset(ao$X, ao$Apr <= aoq1$Apr)
write.csv(aoaprq1, "../output/env/ao_apr_q1.csv")  
aomayq1 <- subset(ao$X, ao$May <= aoq1$May)
write.csv(aomayq1, "../output/env/ao_may_q1.csv")        
aojunq1 <- subset(ao$X, ao$Jun <= aoq1$Jun)
write.csv(aojunq1, "../output/env/ao_jun_q1.csv") 
aojulq1 <- subset(ao$X, ao$Jul <= aoq1$Jul)
write.csv(aojulq1, "../output/env/ao_jul_q1.csv")        
aoaugq1 <- subset(ao$X, ao$Aug <= aoq1$Aug)
write.csv(aoaugq1, "../output/env/ao_aug_q1.csv")  
aosepq1 <- subset(ao$X, ao$Sep <= aoq1$Sep)
write.csv(aosepq1, "../output/env/ao_sep_q1.csv")        
aooctq1 <- subset(ao$X, ao$Oct <= aoq1$Oct)
write.csv(aooctq1, "../output/env/ao_oct_q1.csv") 
aonovq1 <- subset(ao$X, ao$Nov <= aoq1$Nov)
write.csv(aonovq1, "../output/env/ao_nov_q1.csv")        
aodecq1 <- subset(ao$X, ao$Dec <= aoq1$Dec)
write.csv(aodecq1, "../output/env/ao_dec_q1.csv")

aoq1_all <- rbind(aojanq1, aofebq1, aomarq1, aoaprq1, aomayq1, aojunq1, aojulq1, aoaugq1, aosepq1, aooctq1, aonovq1, aodecq1)
write.csv(aoq1_all, "../output/env/ao_q1_all.csv")

@@

aojanq4 <- subset(ao$X, ao$Jan >= aoq4$Jan)
write.csv(aojanq4, "../output/env/ao_jan_q4.csv")        
aofebq4 <- subset(ao$X, ao$Feb >= aoq4$Feb)
write.csv(aofebq4, "../output/env/ao_feb_q4.csv") 
aomarq4 <- subset(ao$X, ao$Mar >= aoq4$Mar)
write.csv(aomarq4, "../output/env/ao_mar_q4.csv")        
aoaprq4 <- subset(ao$X, ao$Apr >= aoq4$Apr)
write.csv(aoaprq4, "../output/env/ao_apr_q4.csv")  
aomayq4 <- subset(ao$X, ao$May >= aoq4$May)
write.csv(aomayq4, "../output/env/ao_may_q4.csv")        
aojunq4 <- subset(ao$X, ao$Jun >= aoq4$Jun)
write.csv(aojunq4, "../output/env/ao_jun_q4.csv") 
aojulq4 <- subset(ao$X, ao$Jul >= aoq4$Jul)
write.csv(aojulq4, "../output/env/ao_jul_q4.csv")        
aoaugq4 <- subset(ao$X, ao$Aug >= aoq4$Aug)
write.csv(aoaugq4, "../output/env/ao_aug_q4.csv")  
aosepq4 <- subset(ao$X, ao$Sep >= aoq4$Sep)
write.csv(aosepq4, "../output/env/ao_sep_q4.csv")        
aooctq4 <- subset(ao$X, ao$Oct >= aoq4$Oct)
write.csv(aooctq4, "../output/env/ao_oct_q4.csv") 
aonovq4 <- subset(ao$X, ao$Nov >= aoq4$Nov)
write.csv(aonovq4, "../output/env/ao_nov_q4.csv")        
aodecq4 <- subset(ao$X, ao$Dec >= aoq4$Dec)
write.csv(aodecq4, "../output/env/ao_dec_q4.csv")

aoq4_all <- rbind(aojanq4, aofebq4, aomarq4, aoaprq4, aomayq4, aojunq4, aojulq4, aoaugq4, aosepq4, aooctq4, aonovq4, aodecq4)
write.csv(aoq4_all, "../output/env/ao_q4_all.csv")
```

>>>>

```{r}
naoraw <- read.csv("../data/env/nao_pc_monthlyX.csv", header = FALSE) 
head(naoraw)
```

lets give some column names. col 1  year, 2:13 are the months
```{r}
colnames(naoraw) <- c("year","Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec", "yr_t")
head(naoraw)
```

@@

naojanq1 <- subset(nao$year, nao$Jan <= naoq1$Jan)
write.csv(naojanq1, "../output/env/nao_jan_q1.csv")        
naofebq1 <- subset(nao$year, nao$Feb <= naoq1$Feb)
write.csv(naofebq1, "../output/env/nao_feb_q1.csv") 
naomarq1 <- subset(nao$year, nao$Mar <= naoq1$Mar)
write.csv(naomarq1, "../output/env/nao_mar_q1.csv")        
naoaprq1 <- subset(nao$year, nao$Apr <= naoq1$Apr)
write.csv(naoaprq1, "../output/env/nao_apr_q1.csv")  
naomayq1 <- subset(nao$year, nao$May <= naoq1$May)
write.csv(naomayq1, "../output/env/nao_may_q1.csv")        
naojunq1 <- subset(nao$year, nao$Jun <= naoq1$Jun)
write.csv(naojunq1, "../output/env/nao_jun_q1.csv") 
naojulq1 <- subset(nao$year, nao$Jul <= naoq1$Jul)
write.csv(naojulq1, "../output/env/nao_jul_q1.csv")        
naoaugq1 <- subset(nao$year, nao$Aug <= naoq1$Aug)
write.csv(naoaugq1, "../output/env/nao_aug_q1.csv")  
naosepq1 <- subset(nao$year, nao$Sep <= naoq1$Sep)
write.csv(naosepq1, "../output/env/nao_sep_q1.csv")        
naooctq1 <- subset(nao$year, nao$Oct <= naoq1$Oct)
write.csv(naooctq1, "../output/env/nao_oct_q1.csv") 
naonovq1 <- subset(nao$year, nao$Nov <= naoq1$Nov)
write.csv(naonovq1, "../output/env/nao_nov_q1.csv")        
naodecq1 <- subset(nao$year, nao$Dec <= naoq1$Dec)
write.csv(naodecq1, "../output/env/nao_dec_q1.csv")
naoalltq1 <- subset(nao$year, nao$yr_t <= naoq1$yr_t)
write.csv(naoalltq1, "../output/env/nao_yrt_q1.csv")

@@

naojanq4 <- subset(nao$year, nao$Jan >= naoq4$Jan)
write.csv(naojanq4, "../output/env/nao_jan_q4.csv")        
naofebq4 <- subset(nao$year, nao$Feb >= naoq4$Feb)
write.csv(naofebq4, "../output/env/nao_feb_q4.csv") 
naomarq4 <- subset(nao$year, nao$Mar >= naoq4$Mar)
write.csv(naomarq4, "../output/env/nao_mar_q4.csv")        
naoaprq4 <- subset(nao$year, nao$Apr >= naoq4$Apr)
write.csv(naoaprq4, "../output/env/nao_apr_q4.csv")  
naomayq4 <- subset(nao$year, nao$May >= naoq4$May)
write.csv(naomayq4, "../output/env/nao_may_q4.csv")        
naojunq4 <- subset(nao$year, nao$Jun >= naoq4$Jun)
write.csv(naojunq4, "../output/env/nao_jun_q4.csv") 
naojulq4 <- subset(nao$year, nao$Jul >= naoq4$Jul)
write.csv(naojulq4, "../output/env/nao_jul_q4.csv")        
naoaugq4 <- subset(nao$year, nao$Aug >= naoq4$Aug)
write.csv(naoaugq4, "../output/env/nao_aug_q4.csv")  
naosepq4 <- subset(nao$year, nao$Sep >= naoq4$Sep)
write.csv(naosepq4, "../output/env/nao_sep_q4.csv")        
naooctq4 <- subset(nao$year, nao$Oct >= naoq4$Oct)
write.csv(naooctq4, "../output/env/nao_oct_q4.csv") 
naonovq4 <- subset(nao$year, nao$Nov >= naoq4$Nov)
write.csv(naonovq4, "../output/env/nao_nov_q4.csv")        
naodecq4 <- subset(nao$year, nao$Dec >= naoq4$Dec)
write.csv(naodecq4, "../output/env/nao_dec_q4.csv") 
naoalltq4 <- subset(nao$year, nao$yr_t >= naoq4$yr_t)
write.csv(naoalltq4, "../output/env/nao_yrt_q4.csv")

@@

aojanq1 <- subset(ao$X, ao$Jan <= aoq1$Jan)
write.csv(aojanq1, "../output/env/ao_jan_q1.csv")        
aofebq1 <- subset(ao$X, ao$Feb <= aoq1$Feb)
write.csv(aofebq1, "../output/env/ao_feb_q1.csv") 
aomarq1 <- subset(ao$X, ao$Mar <= aoq1$Mar)
write.csv(aomarq1, "../output/env/ao_mar_q1.csv")        
aoaprq1 <- subset(ao$X, ao$Apr <= aoq1$Apr)
write.csv(aoaprq1, "../output/env/ao_apr_q1.csv")  
aomayq1 <- subset(ao$X, ao$May <= aoq1$May)
write.csv(aomayq1, "../output/env/ao_may_q1.csv")        
aojunq1 <- subset(ao$X, ao$Jun <= aoq1$Jun)
write.csv(aojunq1, "../output/env/ao_jun_q1.csv") 
aojulq1 <- subset(ao$X, ao$Jul <= aoq1$Jul)
write.csv(aojulq1, "../output/env/ao_jul_q1.csv")        
aoaugq1 <- subset(ao$X, ao$Aug <= aoq1$Aug)
write.csv(aoaugq1, "../output/env/ao_aug_q1.csv")  
aosepq1 <- subset(ao$X, ao$Sep <= aoq1$Sep)
write.csv(aosepq1, "../output/env/ao_sep_q1.csv")        
aooctq1 <- subset(ao$X, ao$Oct <= aoq1$Oct)
write.csv(aooctq1, "../output/env/ao_oct_q1.csv") 
aonovq1 <- subset(ao$X, ao$Nov <= aoq1$Nov)
write.csv(aonovq1, "../output/env/ao_nov_q1.csv")        
aodecq1 <- subset(ao$X, ao$Dec <= aoq1$Dec)
write.csv(aodecq1, "../output/env/ao_dec_q1.csv")  
aoalltq1 <- subset(ao$X, ao$yr_t <= aoq1$yr_t)
write.csv(aoalltq1, "../output/env/ao_yrt_q1.csv")

aoq1_all <- rbind.fill(aojanq1, aofebq1, aomarq1, aoaprq1, aomayq1, aojunq1, aojulq1, aoaugq1, aosepq1, aooctq1, aonovq1, aodecq1, aoalltq1)
write.csv(aoq1_all, "../output/env/ao_q1_all.csv")

@@

aojanq4 <- subset(ao$X, ao$Jan >= aoq4$Jan)
write.csv(aojanq4, "../output/env/ao_jan_q4.csv")        
aofebq4 <- subset(ao$X, ao$Feb >= aoq4$Feb)
write.csv(aofebq4, "../output/env/ao_feb_q4.csv") 
aomarq4 <- subset(ao$X, ao$Mar >= aoq4$Mar)
write.csv(aomarq4, "../output/env/ao_mar_q4.csv")        
aoaprq4 <- subset(ao$X, ao$Apr >= aoq4$Apr)
write.csv(aoaprq4, "../output/env/ao_apr_q4.csv")  
aomayq4 <- subset(ao$X, ao$May >= aoq4$May)
write.csv(aomayq4, "../output/env/ao_may_q4.csv")        
aojunq4 <- subset(ao$X, ao$Jun >= aoq4$Jun)
write.csv(aojunq4, "../output/env/ao_jun_q4.csv") 
aojulq4 <- subset(ao$X, ao$Jul >= aoq4$Jul)
write.csv(aojulq4, "../output/env/ao_jul_q4.csv")        
aoaugq4 <- subset(ao$X, ao$Aug >= aoq4$Aug)
write.csv(aoaugq4, "../output/env/ao_aug_q4.csv")  
aosepq4 <- subset(ao$X, ao$Sep >= aoq4$Sep)
write.csv(aosepq4, "../output/env/ao_sep_q4.csv")        
aooctq4 <- subset(ao$X, ao$Oct >= aoq4$Oct)
write.csv(aooctq4, "../output/env/ao_oct_q4.csv") 
aonovq4 <- subset(ao$X, ao$Nov >= aoq4$Nov)
write.csv(aonovq4, "../output/env/ao_nov_q4.csv")        
aodecq4 <- subset(ao$X, ao$Dec >= aoq4$Dec)
write.csv(aodecq4, "../output/env/ao_dec_q4.csv") 
aoalltq4 <- subset(ao$X, ao$yr_t >= aoq4$yr_t)
write.csv(aoalltq4, "../output/env/ao_yrt_q4.csv")

aoq4_all <- rbind.fill(aojanq4, aofebq4, aomarq4, aoaprq4, aomayq4, aojunq4, aojulq4, aoaugq4, aosepq4, aooctq4, aonovq4, aodecq4, aoalltq4)
write.csv(aoq4_all, "../output/env/ao_q4_all.csv")
```

### 2019-08-30 src/data_exploration.Rmd
laptop update

>>>>

## density plot with background and presence env. data by month

```{r load pres-background dataset}
presback <- read.csv("../output/bio/presab_nafo_yr.csv", header = TRUE)
colnames(presback)
```

this dataset contains a lot of columns you don't need for the maxent models. Remove them here

```{r remove unnecessary columns}
presback <- subset(presback, select = -c(cell_id, id, decimalLatitude, decimalLongitude, datecollected, institutioncode, individualcount, depth, resname, originalscientificname, collectioncode, day, nafo_zone, gear, longitude_meters, latitude_meters, total_cell_obs_xy, total_cell_obs_xyt, bottom_depth, XXtotal_cell_obs_xyzt, temp_celsius_depth, temp_celsius_surface, longitude_meters.1, latitude_meters.1, bottom_depth_glorys, longitude_meters.2, latitude_meters.2, cell_id_3d, total_cell_obs_xyzt, cell_id_xyzt))
colnames(presback)
```

```{r presence by month}

presence <- subset(presback, occurrence == "1")
m1 <- subset(presence, month == "1")
m2 <- subset(presence, month == "2")
m3 <- subset(presence, month == "3")
m4 <- subset(presence, month == "4")
m5 <- subset(presence, month == "5")
m6 <- subset(presence, month == "6")
m7 <- subset(presence, month == "7")
m8 <- subset(presence, month == "8")
m9 <- subset(presence, month == "9")
m10 <- subset(presence, month == "10")
m11 <- subset(presence, month == "11")
m12 <- subset(presence, month == "12")

plot by each variable, less 3m (2 Sample) and 5ze (2 samples)
```{r presence by month by variable}
ggplot(m1, aes(x = temp_surface, colour = month)) + geom_density(na.rm = TRUE) + geom_density(data=m2, na.rm = TRUE) + geom_density(data=m3, na.rm = TRUE) + geom_density(data=m4, na.rm = TRUE) + geom_density(data=m5, na.rm = TRUE) + geom_density(data=m6, na.rm = TRUE) + geom_density(data=m7, na.rm = TRUE) + geom_density(data=m8, na.rm = TRUE) + geom_density(data=m9, na.rm = TRUE) + geom_density(data=m10, na.rm = TRUE) + geom_density(data=m11, na.rm = TRUE) + geom_density(data=m12, na.rm = TRUE)
dev.copy(png,"../output/env/env_by_month_plots/temp_surface_month.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(m1, aes(x = temp_depth, colour = month)) + geom_density(na.rm = TRUE) + geom_density(data=m2, na.rm = TRUE) + geom_density(data=m3, na.rm = TRUE) + geom_density(data=m4, na.rm = TRUE) + geom_density(data=m5, na.rm = TRUE) + geom_density(data=m6, na.rm = TRUE) + geom_density(data=m7, na.rm = TRUE) + geom_density(data=m8, na.rm = TRUE) + geom_density(data=m9, na.rm = TRUE) + geom_density(data=m10, na.rm = TRUE) + geom_density(data=m11, na.rm = TRUE) + geom_density(data=m12, na.rm = TRUE)
dev.copy(png,"../output/env/env_by_month_plots/temp_depth_month.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(m1, aes(x = chl_surface, colour = month)) + geom_density(na.rm = TRUE) + geom_density(data=m2, na.rm = TRUE) + geom_density(data=m3, na.rm = TRUE) + geom_density(data=m4, na.rm = TRUE) + geom_density(data=m5, na.rm = TRUE) + geom_density(data=m6, na.rm = TRUE) + geom_density(data=m7, na.rm = TRUE) + geom_density(data=m8, na.rm = TRUE) + geom_density(data=m9, na.rm = TRUE) + geom_density(data=m10, na.rm = TRUE) + geom_density(data=m11, na.rm = TRUE) + geom_density(data=m12, na.rm = TRUE)
dev.copy(png,"../output/env/env_by_month_plots/chl_surface_month.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(m1, aes(x = chl_depth, colour = month)) + geom_density(na.rm = TRUE) + geom_density(data=m2, na.rm = TRUE) + geom_density(data=m3, na.rm = TRUE) + geom_density(data=m4, na.rm = TRUE) + geom_density(data=m5, na.rm = TRUE) + geom_density(data=m6, na.rm = TRUE) + geom_density(data=m7, na.rm = TRUE) + geom_density(data=m8, na.rm = TRUE) + geom_density(data=m9, na.rm = TRUE) + geom_density(data=m10, na.rm = TRUE) + geom_density(data=m11, na.rm = TRUE) + geom_density(data=m12, na.rm = TRUE)
dev.copy(png,"../output/env/env_by_month_plots/chl_depth_month.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(m1, aes(x = salinity_surface, colour = month)) + geom_density(na.rm = TRUE) + geom_density(data=m2, na.rm = TRUE) + geom_density(data=m3, na.rm = TRUE) + geom_density(data=m4, na.rm = TRUE) + geom_density(data=m5, na.rm = TRUE) + geom_density(data=m6, na.rm = TRUE) + geom_density(data=m7, na.rm = TRUE) + geom_density(data=m8, na.rm = TRUE) + geom_density(data=m9, na.rm = TRUE) + geom_density(data=m10, na.rm = TRUE) + geom_density(data=m11, na.rm = TRUE) + geom_density(data=m12, na.rm = TRUE)
dev.copy(png,"../output/env/env_by_month_plots/salinity_surface_month.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(m1, aes(x = salinity_depth, colour = month)) + geom_density(na.rm = TRUE) + geom_density(data=m2, na.rm = TRUE) + geom_density(data=m3, na.rm = TRUE) + geom_density(data=m4, na.rm = TRUE) + geom_density(data=m5, na.rm = TRUE) + geom_density(data=m6, na.rm = TRUE) + geom_density(data=m7, na.rm = TRUE) + geom_density(data=m8, na.rm = TRUE) + geom_density(data=m9, na.rm = TRUE) + geom_density(data=m10, na.rm = TRUE) + geom_density(data=m11, na.rm = TRUE) + geom_density(data=m12, na.rm = TRUE)
dev.copy(png,"../output/env/env_by_month_plots/salinity_depth_month.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(m1, aes(x = o2_surface, colour = month)) + geom_density(na.rm = TRUE) + geom_density(data=m2, na.rm = TRUE) + geom_density(data=m3, na.rm = TRUE) + geom_density(data=m4, na.rm = TRUE) + geom_density(data=m5, na.rm = TRUE) + geom_density(data=m6, na.rm = TRUE) + geom_density(data=m7, na.rm = TRUE) + geom_density(data=m8, na.rm = TRUE) + geom_density(data=m9, na.rm = TRUE) + geom_density(data=m10, na.rm = TRUE) + geom_density(data=m11, na.rm = TRUE) + geom_density(data=m12, na.rm = TRUE)
dev.copy(png,"../output/env/env_by_month_plots/o2_surface_month.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(m1, aes(x = o2_depth, colour = month)) + geom_density(na.rm = TRUE) + geom_density(data=m2, na.rm = TRUE) + geom_density(data=m3, na.rm = TRUE) + geom_density(data=m4, na.rm = TRUE) + geom_density(data=m5, na.rm = TRUE) + geom_density(data=m6, na.rm = TRUE) + geom_density(data=m7, na.rm = TRUE) + geom_density(data=m8, na.rm = TRUE) + geom_density(data=m9, na.rm = TRUE) + geom_density(data=m10, na.rm = TRUE) + geom_density(data=m11, na.rm = TRUE) + geom_density(data=m12, na.rm = TRUE)
dev.copy(png,"../output/env/env_by_month_plots/o2_depth_month.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(m1, aes(x = mlp_surface, colour = month)) + geom_density(na.rm = TRUE) + geom_density(data=m2, na.rm = TRUE) + geom_density(data=m3, na.rm = TRUE) + geom_density(data=m4, na.rm = TRUE) + geom_density(data=m5, na.rm = TRUE) + geom_density(data=m6, na.rm = TRUE) + geom_density(data=m7, na.rm = TRUE) + geom_density(data=m8, na.rm = TRUE) + geom_density(data=m9, na.rm = TRUE) + geom_density(data=m10, na.rm = TRUE) + geom_density(data=m11, na.rm = TRUE) + geom_density(data=m12, na.rm = TRUE)
dev.copy(png,"../output/env/env_by_month_plots/mlp_month.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(m1, aes(x = ssh_surface, colour = month)) + geom_density(na.rm = TRUE) + geom_density(data=m2, na.rm = TRUE) + geom_density(data=m3, na.rm = TRUE) + geom_density(data=m4, na.rm = TRUE) + geom_density(data=m5, na.rm = TRUE) + geom_density(data=m6, na.rm = TRUE) + geom_density(data=m7, na.rm = TRUE) + geom_density(data=m8, na.rm = TRUE) + geom_density(data=m9, na.rm = TRUE) + geom_density(data=m10, na.rm = TRUE) + geom_density(data=m11, na.rm = TRUE) + geom_density(data=m12, na.rm = TRUE)
dev.copy(png,"../output/env/env_by_month_plots/ssh_month.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png
```

```{r}
presence$month <- factor(presence$month, order = TRUE, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12"))

ggplot(presence, aes(temp_depth, colour = month)) + geom_density()
dev.copy(png,"../output/env/env_by_month_plots/temp_depth_month.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(presence, aes(salinity_depth, colour = month)) + geom_density()
dev.copy(png,"../output/env/env_by_month_plots/salinity_depth_month.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(presence, aes(o2_depth, colour = month)) + geom_density()
dev.copy(png,"../output/env/env_by_month_plots/o2_depth_month.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(presence, aes(chl_surface, colour = month)) + geom_density()
dev.copy(png,"../output/env/env_by_month_plots/chl_surface_month.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

back <- subset(presback, occurrence == "0")

back$month <- factor(back$month, order = TRUE, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12"))

ggplot(back, aes(temp_depth, colour = month)) + geom_density()
dev.copy(png,"../output/env/env_by_month_plots/temp_depth_month_background.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(back, aes(salinity_depth, colour = month)) + geom_density()
dev.copy(png,"../output/env/env_by_month_plots/salinity_depth_month_background.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(back, aes(o2_depth, colour = month)) + geom_density()
dev.copy(png,"../output/env/env_by_month_plots/o2_depth_month_background.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(back, aes(chl_surface, colour = month)) + geom_density()
dev.copy(png,"../output/env/env_by_month_plots/chl_surface_month_background.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png
```

### 2019-08-30 src/maxent_alldata_avec_xvalidation.Rmd
laptop update

add land to plots with standard legend (working code) THIS WORK!!!
```{r}
aea <- raster("../output/env/aea.tif") #the correct CRS
maplst <- list.files("../output/maxent/all_data/predictions/", pattern = "binary_avg_2d.*.asc", full.names = TRUE)
s <- shapefile("../data/env/landp/landpro.shp") #made in arcgis
apr <- aea@crs
#brk <- seq(0.1, 1, 0.1) #for legend
redtrans <- rgb(218, 215, 216, 90, maxColorValue=255) 
outsidemcp <- shapefile("../data/env/landp/mcpout.shp") #made in arcgis

@@

for (pred in 1:length(maplst)){
  pras <- raster(maplst[pred])
  crs(pras) <- apr
  ascname <- names(pras)
  pras[pras >0] <- 1
  lp <- plot(pras, breaks=brk, col=rev(colorRampPalette(brewer.pal(10, "Spectral"))(10)), axes = FALSE, box = FALSE, legend = FALSE)
  lp <- plot(pras)
  lp <- plot(outsidemcp,  col = redtrans, border = redtrans, add = TRUE)
  lp <- plot(s, col = "#474646", border = "#474646", add = TRUE)
  print(lp)
  dev.copy(png, (paste0("../output/maxent/all_data/predictions/", ascname, pred, ".png")), width = 1920,height = 1080)
  dev.off() # stops automatic saving of the plot to a png))
}

>>>>

add land to plots with standard legend (working code) THIS WORK!!!
```{r}
aea <- raster("../output/env/aea.tif") #the correct CRS
maplst <- list.files("../output/maxent/all_data/predictions/apr", pattern = "binary_avg_2d.*.asc", full.names = TRUE)
s <- shapefile("../data/env/landp/landpro.shp") #made in arcgis
apr <- aea@crs
brk <- seq(0.1, 1, 0.1) #for legend
redtrans <- rgb(218, 215, 216, 90, maxColorValue=255) 
outsidemcp <- shapefile("../data/env/landp/mcpout.shp") #made in arcgis

@@

for (pred in 1:length(maplst)){
  pras <- raster("../output/maxent/all_data/predictions/apr/avg_47.2119.asc")
  crs(pras) <- apr
  ascname <- names(pras)
  #pras[pras >0] <- 1
  lp <- plot(pras, breaks=brk, col=rev(colorRampPalette(brewer.pal(10, "Spectral"))(10)), axes = FALSE, box = FALSE, legend = TRUE)
  lp <- plot(pras)
  lp <- plot(outsidemcp,  col = redtrans, border = redtrans, add = TRUE)
  lp <- plot(s, col = "#474646", border = "#474646", add = TRUE)
  print(lp)
 # dev.copy(png, (paste0("../output/maxent/all_data/predictions/", ascname, pred, ".png")), width = 1920,height = 1080)
  #dev.off() # stops automatic saving of the plot to a png))
}
